%-------------------------
% Resume in Latex
% Original author: https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://vietch2612.github.io/}{\Large Viet Cao}} & Email: \href{mailto:viet.ch2612@gmail.com}{viet.ch2612@gmail.com}\\
   Product Manager, Product Owner & Mobile : \href{tel:+84938922612}{+84-938-922-612} \\
   Ho Chi Minh City, Viet Nam & \href{http://vietch2612.github.io}{http://vietch2612.github.io/} \\
   {} & \href{https://www.linkedin.com/in/vietch2612/}{https://www.linkedin.com/in/vietch2612/} \\
   {} & \small{\textit{Last updated: February 2023}} \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
  {A Product Manager with over 6 years of experience, three times and twice in a row is the most contributing employee of the year. Extensive experience in software development lifecycle, end-to-end product management, Agile methodology and practices.}

%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {OP3N LLC.}{Ho Chi Minh City, Viet Nam and LA, US}
      {Product Manager}{May 2022 - Dec 2022 (8 months)}
      \resumeItemListStart
        \resumeItem{Product}
            {Collaborate with the US team to build a Web3 platform, to help creators to create, own and connect their ideas to the community. Website: \underline{\href{https://op3n.world.}{https://op3n.world.}}}
        \resumeItem{Product Development}
            {Research, define user stories and technical specifications for the platform such as NFT Minting, NFT Social Marketplace, NFT-Gated Ticketing, NFT-Gated Merch Store.}
        \resumeItem{Product Management}
            {Take ownership of the software/product development life cycle SDLC, product strategy, roadmap, development and the launching of the product. Work closely with business stakeholders and technical developers for prioritization, make decision on strategic approach and product development.}
        \resumeItem{Agile/Scrum}
            {Coach, work closely with the Scrum team for the product roadmap, backlog, sprints, and to build the working/development processes.}
      \resumeItemListEnd

    \resumeSubheading
      {7-Eleven Viet Nam}{Ho Chi Minh City, Viet Nam}
      {Tech Product Manager}{March 2017 - May 2022 (5 years 3 months)}
      \resumeItemListStart
        \resumeItem{Product Development}
        {Lead the Enterprise development team to build the core system including Point of Sales, Order and Delivering, Operation, Warehouse Management System and many more. 7-Eleven VN is one of the few countries out of 19 in the world that can build its own System. An extremely massive and complex system but opens up more opportunities than buying an existing one.}
        \resumeItem{Product Development}
        {Lead the Consumer development team to build headless e-commerce services, integrating our system with other e-payment systems and e-commerce sites like GoJek, GrabFood and more. This team has turned 7-Eleven into a store that customers can pay with almost any form of payment or can be seen in any online food ordering service available in Ho Chi Minh City.}
        \resumeItem{Collaboration}
        {Coordination and collaboration in multiple departments together to deliver products from concept to end-user.}
        \resumeItem{Analytics}
        {Identify and analyze product problems to propose solutions based on data and customer's feedback to improve, increase stability and user experience.}
        \resumeItem{Scrum Master}
        {Apply and maintain the Scrum principles, development process best practices. Set up and improve process/workflow for the development team on Jira, Confluence to maximize team's productivity. Teach Scrum practices and principles to the broader organization.}
        \resumeItem{Digital Transformation}
        {Develop, create and improve internal business processes across departments with new technologies, transform operational processes into digital platforms that reduce errors, increase efficiency, and reduce errors.}
    \resumeItemListEnd

    \resumeSubheading
      {Silicon Straits Saigon}{Ho Chi Minh City, Viet Nam}
      {QA Engineer}{October 2015 - February 2017 (1 year 5 months)}
      \resumeItemListStart
        \resumeItem{Quality assurance}
            {Basic day-to-day tasks as a Quality engineer such as requirements analysis, defining checklists, test cases, test plans, and test execution to control the quality of several internal projects to ensure the quality of the team in terms of the project's output and working process.}
        \resumeItem{End-to-end automation testing}
            {Implement automation test scripts using Calabash, Appium, JMeter, Selenium, TestNG to run on AWS DeviceFarm. Implement the alerting system to make sure the system is alive.}
        \resumeItem{Scrum Master}
            {Coach team members, assist the PM by incorporating techniques to improve processes.}
      \resumeItemListEnd

\pagebreak

    \resumeSubheading
      {GNT Viet Nam}{Ho Chi Minh City, Viet Nam}
      {QC Engineer}{October 2013 - September 2015 (2 years)}
      \resumeItemListStart
        \resumeItem{Quality control}
            {Defining checklists, test cases, test plans and test execution in order to control the quality of the product.}
        \resumeItem{End-to-end automation testing}
            {Implement automation test script using Selenium with Java and TestNG framework.}
        \resumeItem{Performance testing}
            {Create the performance test strategies, test scripts using JMeter and Jenkins.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------AWARD-----------------
\section{Award}
  \resumeSubHeadingListStart
    \resumeSubItem{Shining stars of the year 2019, Contributor of the year 2020}
        {Awarded by 7-Eleven Viet Nam to the individual who makes the most contributions and demonstrates the company's values.}
    \resumeSubItem{Pirate of the month 2016}
        {Awarded by Silicon Straits Saigon to the most outstanding employee of the month.}
    \resumeSubItem{Excellent employee of the year 2014}
        {Awarded by GNT Viet Nam for the most dedicated employee of the year.}
  \resumeSubHeadingListEnd

%-----------LICENCES & CERTIFICATES-----------------
\section{Licence and Certificate}
  \resumeSubHeadingListStart
    \resumeSubItem{Google Project Management Certificate}
      {Offered by Google Professional Certificates, issued by Coursera} \href{https://www.coursera.org/account/accomplishments/specialization/certificate/HUB6LA4G4WHF}{\underline{\textit{(View certificate)}}}
    \resumeSubItem{Project Management Principles and Practices Specialization}
      {Offered by University of California, Irvine, issued by Coursera}\href{https://www.coursera.org/account/accomplishments/specialization/certificate/T7KQFGHZX4J2}{\underline{\textit{(View certificate)}}}
    \resumeSubItem{Agile with Atlassian Jira}
      {Offered by Atlassian University, issued by Coursera}\href{https://www.coursera.org/account/accomplishments/certificate/K3PXCZCWU8FV}{\underline{\textit{(View certificate)}}}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ho Chi Minh City University of Science}{Ho Chi Minh City, Viet Nam}
      {Bachelor in Information Technology}{September 2022 -- 2024}
    \resumeSubheading
      {University of Transport Technology}{Thai Nguyen, Viet Nam}
      {Associate of Degree in Information Technology}{September 2010 -- May 2013}
  \resumeSubHeadingListEnd


%-----------ARTICLES-----------------
\section{Published article}
  \resumeSubHeadingListStart
    \resumeSubItem{Vietnamese}
        {How 7LAB at 7-Eleven using Jira to enhance the development workflows. }\href{https://medium.com/7-lab/bddb5245a522}{\underline{\textit{(Read)}}}
    \resumeSubItem{Vietnamese}
        {Why Jira Service Desk instead of Zendesk?}\href{https://medium.com/7-lab/b664667aa90d}{\underline{\textit{(Read)}}}
  \resumeSubHeadingListEnd

%-----------INTEREST-----------------
\section{Interest}
\resumeSubHeadingListStart
  \resumeSubItem{Reading}
    {I love fiction, novels, and biography. I also enjoy reading articles on Medium or other internet sources. This is the way I keep my mind fresh and maintain my knowledge.}
  \resumeSubItem{Mechanical Keyboards}
    {It is my personal hobby. I really like mechanical keyboards. I love the feeling when my fingers are dancing on the keycaps and made thocky sounds out of them. If you don't have one, you should try it.}
\resumeSubHeadingListEnd

%-----------REFERENCES-----------------
\section{Recommendation}
    \resumeSubHeadingListStart
        \resumeSubItem{Trung Luong - Tech Director at 7-Eleven Viet Nam}
            {I was pleased to work with Viet as the product manager. He is an outstanding professional and always puts in the extra effort to ensure that the team delivers the best results. Viet is an incredible team player, always willing to help out his colleagues and share his knowledge. He is also highly motivated and has an infectious enthusiasm for his work. His dedication, hard work, and serious attitude make him an ideal candidate for any position that requires a high level of commitment.}
         \resumeSubItem{Nghia Lam - Product Director at OP3N LLC}
            {Viet is one of the rare all-rounded Product Manager. He can work on almost any stages in building a successful product, with great efficiency. He can also offer great helps setting up and managing the working process in a tech team, ensuring the deliverables quality is met and the product can be launched in a timely manner. I’m confident that Viet would be a valuable member in any team he joins in the future.}
        \resumeSubItem{Tuan Luu - Head of Engineering at 7-Eleven Viet Nam}
            {I was so happy when working with Viet. He has a stable personality and high sense of responsibility. He always guarantee the project progress. Besides he often share knowledge with the team.}
    \resumeSubHeadingListEnd
    {Please look at the completed list of recommendations on my LinkedIn profile page.} \href{https://www.linkedin.com/in/vietch2612/details/recommendations/?detailScreenTabIndex=0}{\underline{\textit{(Visit)}}}


%-------------------------------------------
\end{document}